Fluent statistical computing interfaces for biological data analysis

### 2020-08-03 Rmd/04-intron.Rmd
addresses comments and closes #10

```{r si-cvg-ccdc43, echo=FALSE, fig.cap = "(ref:si-cvg-ccdc43)", out.width="80%"}
knitr::include_graphics(here::here("img", "ccdc43.pdf"))
```

(ref:si-cvg-nat15) The gene nat15 exhibits another example of U12 intron retention (located at around 27.93Mb) in the rnpc3 knockout groups.

```{r si-cvg-nat15,  echo=FALSE, fig.cap = "(ref:si-cvg-nat15)", out.width="80%"}
knitr::include_graphics(here::here("img", "nat15.pdf"))
```

@@

```{r si-cvg-mapk3,  echo=FALSE, fig.cap = "(ref:si-cvg-mapk3)", out.width="80%"}
knitr::include_graphics(here::here("img", "mapk3.pdf"))
```

@@

```{r si-cvg-tspan31, echo=FALSE, fig.cap = "(ref:si-cvg-tspan31)", out.width="80%"}
knitr::include_graphics(here::here("img", "tspan31.pdf"))
```

>>>>

```{r si-cvg-ccdc43, echo=FALSE, fig.cap = "(ref:si-cvg-ccdc43)", out.width="80%"}
ext <- ifelse(knitr::is_latex_output(), ".pdf", ".png")

knitr::include_graphics(here::here("img", paste0("ccdc43", ext)))
```

(ref:si-cvg-nat15) The gene nat15 exhibits another example of U12 intron retention, located at around 27.93Mb, in the rnpc3 knockout groups.

```{r si-cvg-nat15,  echo=FALSE, fig.cap = "(ref:si-cvg-nat15)", out.width="80%"}
knitr::include_graphics(here::here("img", paste0("nat15", ext)))
```

@@

```{r si-cvg-mapk3,  echo=FALSE, fig.cap = "(ref:si-cvg-mapk3)", out.width="80%"}
knitr::include_graphics(here::here("img", paste0("mapk3", ext)))
```

@@

```{r si-cvg-tspan31, echo=FALSE, fig.cap = "(ref:si-cvg-tspan31)", out.width="80%"}
knitr::include_graphics(here::here("img", paste0("tspan31", ext)))
```
